---
title: "Lab2"
author: "Kaden DuBois"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
---

# Tasks
## Task 1
### Get working directory
```{r}
getwd()
```

## Task 2
### Read the EPAGAS.csv file into R
```{r}
epagas <- read.csv('EPAGAS.csv')
```

### Obtain the first 6 entries of Epagas
```{r}
head(epagas)
```

## Task 3
### Make the object mpg, a miles per galon vector
```{r}
mpg=epagas$MPG
```

### Transform the mpg to z
```{r}
z=(mpg-mean(mpg))/sd(mpg)
```

Verify that the mean value of z is 0
```{r}
mean(z)
```

Verify that the standard deviation of z squared is 1
```{r}
sd(z)^2
```

### Find the values of mpg that are possible outliers using z
```{r}
mpg[abs(z)>=2 & abs(z)<=3]
```

### Find the values of mpg that are defined as outliers
```{r}
mpg[abs(z)>3]
```

### Construct a dotplot of mpg with colors
```{r}
library(lattice)
dotcol = ifelse(abs(z)>3, "Red",
          ifelse(abs(z)>=2 & abs(z)<=3,"Blue", 
            "Black"))
dotplot(mpg, col=dotcol)
```

## Task 4
### Make a boxplot of the MPG varaiable meeting specifications
```{r}
library(ggplot2)
ggplot(epagas, aes(x='',y=mpg)) + 
  geom_boxplot(fill='Black', notch=TRUE) + coord_flip() + ggtitle("Miles Per Gallon - Kaden DuBois")
```

### Use Chebyshev’s theorem to predict the proportion of data within 2 standard deviations of the mean

3/4 of the data should be within 2 standard deviations of the mean

### Calculate the exact proportion within 2 standard deviation of the mean
```{r}
length(mpg[abs(z)<2])/length(mpg)
```

### Does Chebyshev agree with the data?

Chebyshev's theorem agrees with the data. Over 75% of the data is within 2 Standard Deviations.

### Use the emperical rule to predict the proportion of data within 2 standard deviations of the mean

The emperical rule states that approximately 95% of the data should be within 2 standard deviations of the mean.

### How well does it correspond?

The emperical rule corresponds almost exactly to the actual value that is calculated.

### Is the emperical rule valid in this case?
We can use a histogram to visualize the distribution of the data.
```{r}
ggplot(epagas,aes(x=MPG)) + geom_histogram()
```  

Looking at this histogram, we can see that the data is approximately symmetrical and mound shaped. Because of this distribution, the emperical rule is valid to use in this case.
