---
title: "Lab 5"
author: "Kaden DuBois"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks 
## Task 1
```{r}
getwd()
```

## Task 2
### Mybin function
```{r}
mybin=function(iter=100,n=10, p=0.5){ 
sam.mat=matrix(NA,nr=n,nc=iter, byrow=TRUE)
succ=c()
for( i in 1:iter){
sam.mat[,i]=sample(c(1,0),n,replace=TRUE, prob=c(p,1-p))
succ[i]=sum(sam.mat[,i])
}
succ.tab=table(factor(succ,levels=0:n))
barplot(succ.tab/(iter), col=rainbow(n+1), main="Binomial simulation", xlab="Number of successes")
succ.tab/iter
}
```

### iter=100
```{r}
mybin(iter=100,n=10,p=0.7)
```

### iter=200
```{r}
mybin(iter=200,n=10,p=0.7)
```

### iter=500
```{r}
mybin(iter=500,n=10,p=0.7)
```

### iter=1000
```{r}
mybin(iter=1000,n=10,p=0.7)
```

### iter=10000
```{r}
bin10000 = mybin(iter=10000,n=10,p=0.7)
```

### iter=10000 table
```{r}
bin10000
```

### Verify using dbinom()
```{r}
dbin.tab = round(dbinom(0:10, size=10, prob = 0.7), 4)
names(dbin.tab) = 0:10
dbin.tab
```

The numbers in the iter=10000 table and the dbinom function are approximately the same, meaning it is correct.

## Task 3
### Marbles without replacement
```{r}
sample(c(1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0), size = 5, replace=FALSE, prob=NULL)
```

### Marbles with replacement
```{r}
sample(c(1,1,1,1,1,1,1,1,1,1,1,1,0,0,0,0,0,0,0,0), size = 5, replace=TRUE, prob=NULL)
```

### MyHyper function
```{r}
myhyper=function(iter=100,N=20,r=12,n=5){
sam.mat=matrix(NA,nr=n,nc=iter, byrow=TRUE)
succ=c()
for( i in 1:iter){
sam.mat[,i]=sample(rep(c(1,0),c(r,N-r)),n,replace=FALSE)
succ[i]=sum(sam.mat[,i])
}
succ.tab=table(factor(succ,levels=0:n))
barplot(succ.tab/(iter), col=rainbow(n+1), main="HYPERGEOMETRIC simulation", xlab="Number of successes")
succ.tab/iter
}
```

### iter=100
```{r}
myhyper(iter=100,N=20,r=12,n=5)
```

### iter=200
```{r}
myhyper(iter=200,N=20,r=12,n=5)
```

### iter=500
```{r}
myhyper(iter=500,N=20,r=12,n=5)
```

### iter=1000
```{r}
myhyper(iter=1000,N=20,r=12,n=5)
```

### iter=10000
```{r}
hyper10000 = myhyper(iter=10000,N=20,r=12,n=5)
```

### iter=10000 table
```{r}
hyper10000
```

### Verify using dhyper()
```{r}
dhyp.tab = round(dhyper(x = 0:5, m = 12, n = 8, k = 5), 4)
names(dhyp.tab) = 0:5
dhyp.tab
```

The numbers in the iter=10000 table and the table given by dhyper are approximately the same, which means that it is correct.

## Task 4

The mysample() function appears to be similar to the normal sample() function. The values are between one and ten and are replaced after they are chosen. The function needs inputs for the number of iterations and the time you want to elapse before the table is released and the next iteration starts.

### MySample function
```{r}
mysample=function(n, iter=10,time=0.5){
for( i in 1:iter){
s=sample(1:10,n,replace=TRUE)
sf=factor(s,levels=1:10)
barplot(table(sf)/n,beside=TRUE,col=rainbow(10), 
main=paste("Example sample()", " iteration ", i, " n= ", n,sep="") ,
ylim=c(0,0.2)
)
Sys.sleep(time)
}
}
```

### Run the function with the given parameters
Changed this to 1 since only 1 is needed.
```{r}
mysample(n = 1000, iter=1, time=1)
```

### Describe what happened
The output is an animation of bargraphs that shows the distribution which is very close to 0.10 for all 10 of the values.

## Task 5
### Calculate (8 4)
```{r}
choose(8,4)
```

### P(Y>4),Y~Pois(λ=2)
```{r}
1 - ppois(q = 3, lambda = 2)
```

### P(Y=10),Y~NegBin(p=0.4,r=3)
```{r}
choose(10 - 1, 3 - 1) * 0.4 ^ 3 * 0.6 ^ (10 - 3)
```

###  P(Y≤8),Y~Bin(n=15,p=0.4)
```{r}
pbinom(q = 8, size = 15, prob=0.4)
```

## Task 6
```{r}
library(devtools)
devtools::install("C:/RPACKAGES/KDDMATH4753")
library(KDDMATH4753)
t.bin <- KDDMATH4753::mybin(iter=1000, n=10, p=0.5)
t.bin
```