---
title: "Lab1"
author: "Kaden DuBois"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks

## Task 1

```{r}
getwd()
```

## Task 2

```{r}
ddt <- read.csv("DDT-1.csv")
head(ddt)
```

## Task 3

### Qualitative Variables
```{r}
cat('RIVER', 'SPECIES')
```

### Quantitative Variables
```{r}
cat('MILE', 'LENGTH', 'WIDTH', 'DDT')
```

### Number of Species
```{r}
numSpec <- length(unique(ddt$SPECIES))
cat(numSpec)
```

### LMBASS bigger than 800gms
```{r}
with(ddt, ddt[SPECIES == 'LMBASS' & WEIGHT > 800,])
```

### DDT bigger than 4.0 in SCM river
```{r}
with(ddt, ddt[RIVER == 'SCM' & DDT > 4.0,])
```

## Task 4
### Mean Length of Fish
```{r}
mean(ddt$LENGTH)
```

### Standard Deviation of the Weight of Fish
```{r}
sd(ddt$WEIGHT)
```

## Task 5
### Make a table of the rivers
```{r}
riverTable=table(ddt$RIVER)
```

### Make a color coded barplot of the rivers table
```{r}
barplot(riverTable,beside=TRUE,col=rainbow(4))
```

### Table of the rivers crossed with the species of fish
```{r}
riverSpecies=table(ddt$RIVER,ddt$SPECIES)
```

### Color coded barplot of the crossed table
```{r}
barplot(riverSpecies,beside=TRUE,col=rainbow(4))
```

## Task 6
### Piechart of fish Species
```{r}
pie(with(ddt,table(SPECIES)))
```

### Piechart of Rivers
```{r}
pie(with(ddt,table(RIVER)))
```

## Task 7
### Boxplot of the variable DDT
```{r}
with(ddt,boxplot(DDT))
```

### Boxplot of the variable WEIGHT
```{r}
with(ddt,boxplot(WEIGHT))
```

### Boxplot of the variable LENGTH
```{r}
with(ddt,boxplot(LENGTH))
```

## Task 8
### Coplot of LENGTH vs WIDTH given RIVER
```{r}
with(ddt,coplot(LENGTH~WEIGHT|RIVER))
```

### Coplot of DDT vs WEIGHT given SPECIES
```{r}
with(ddt,coplot(DDT~WEIGHT|SPECIES))
```

## Task 9
### ggplot boxplot
```{r}
library(ggplot2)
ggplot(ddt, aes(x = SPECIES,
                y = WEIGHT,
                fill = RIVER)) + 
  geom_boxplot() + ggtitle('Kaden DuBois')

```

### ggplot violin plot
```{r}
library(ggplot2)
ggplot(ddt, aes(x = RIVER,
                y = LENGTH,
                fill = SPECIES)) +
  geom_violin() + ggtitle('Kaden DuBois')
```

### ggplot scatter plot
```{r}
library(ggplot2)
ggplot(ddt, aes(x = WEIGHT,
                y = LENGTH,
                color = SPECIES)) +
  geom_point() + ggtitle('Kaden DuBois')
```

