---
title: "Lab4"
author: "Kaden DuBois"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
---

# Tasks
## Task 1
```{r}
getwd()
```

## Task 2
```{r}
spruce.df <- read.csv('SPRUCE.csv')
tail(spruce.df)
```

## Task 3
### Lowess Smooth Scatter Plot
```{r}
library(s20x)
trendscatter(Height~BHDiameter,f=0.5,data=spruce.df)
```

### Make Lineaer Model Object
```{r}
spruce.lm=with(spruce.df,lm(Height~BHDiameter))
```

### Find the Residuals and Fitted Values
```{r}
height.res=residuals(spruce.lm)
height.fit=fitted(spruce.lm)
```

### Plot the Residuals vs Fitted 
```{r}
plot(height.fit,height.res)
```

### Plot the Residuals vs Fitted with a Lowess Smooth Scatter Plot
```{r}
trendscatter(height.fit,height.res)
```

### Analyze and Compare Plots
The plot of the residuals vs the fitted shows a mound type curve. The original trend scatter plot shows a line that continuously increases throughout the plot.

### Make the Residual plot
```{r}
plot(spruce.lm, which=1)
```

### Check Normality
```{r}
normcheck(spruce.lm,shapiro.wilk = TRUE)
```

### What is the P-value in the Shapiro-Wilks test? What is the NULL hypothesis?
The P-value from this Shapiro-Wilks test is 0.29. The NULL hypothesis is that the data is distributed normally.

## Task 4
### Fit a quadratic to the points
```{r}
quad.lm=lm(Height~BHDiameter + I(BHDiameter^2),data=spruce.df)
```

### Make a fresh Scatter plot and add the quadratic to it
```{r}
plot(Height~BHDiameter,bg="Blue",pch=21,cex=1.2,
ylim=c(0,max(Height)),xlim=c(0,max(BHDiameter)), 
main="Spruce height prediction",data=spruce.df)
coef(quad.lm)
myplot=function(x){
 0.86089580 +1.46959217*x  -0.02745726*x^2
}
curve(myplot, lwd=2, col="steelblue",add=TRUE)
```

### Make quad.fit, a vector of fitted values.
```{r}
quad.fit=fitted(quad.lm)
```

### Make a plot of the residuals vs fitted values.
```{r}
quad.res=residuals(quad.lm)
plot(quad.fit, quad.res)
``` 

### Construct a QQ plot
```{r}
normcheck(quad.lm,shapiro.wilk = TRUE)
```

### What is the P-value of the test? What do you conclude?
Te P-value of the test is 0.684. I conclude that the distribution is normal because the P-value is above 0.05.

## Task 5
### Summarize quad.lm
```{r}
summary(quad.lm)
```

### What is the value of B0?
The value of B0 is 0.860896.

### What is the value of B1?
The value of B1 is 1.469592.

### What is the value of B2?
The value of B2 is -0.027457.

### Make interval estimates for B0, B1, and B2
```{r}
ciReg(quad.lm)
```

### Write down the equation for the fitted line.
$Y = 0.860896 + 1.469592x - 0.027457$

### Predict the Height of spruce when the Diameter is 15, 18 and 20cm
```{r}
predict(quad.lm, data.frame(BHDiameter=c(15,18,20)))
```

### Compare to prior predictions.
