---
title: "Lab 8"
author: "Kaden DuBois"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Tasks

## Task 1: Working Directory
```{r}
getwd()
```

## Task 2: 
### Sample Creation
```{r}
sample = runif(10, 0, 5)
sample
```

### Mean and Variance of Population
```{r}
muPop = (0 + 5) / 2
vPop = (5 - 0)^2 / 12
c(muPop, vPop)
```

### Mean and Variance of Sample
```{r}
muSam = mean(sample)
vSam = var(sample)
c(muSam, vSam)
```

### Comparing Population and Sample
The mean and variance of the sample is usually close to the mean and variance of the population, sometimes it is slightly larger or smaller.

### myclt function
```{r}
myclt=function(n,iter){
  y=runif(n*iter,0,5) # A
  data=matrix(y,nr=n,nc=iter,byrow=TRUE) #B
  sm=apply(data,2,sum) #C
  hist(sm)
  sm
}
# w=myclt(n=10,iter=10000) #D
```

### myclt explanation
When line A is run, a sample is created with the size of n * iter  
When line B is run, the sample is stored in a matrix with n rows and iter columns, breaking up the data.  
When line C is run, the information in the columns is summed together  
When line D is run, the function will run with n = 10 and iter = 10000 and a histogram of the sums will be created  

### Example plot
```{r}
w = myclt(n = 10, iter = 10000)
```

### Mean and variance of w
```{r}
muW = mean(w)
vW = var(w)
c(muW, vW)
```

### Modify function to return mean rather than sum
```{r}
meanclt=function(n,iter){
  y=runif(n*iter,0,5) # A
  data=matrix(y,nr=n,nc=iter,byrow=TRUE) #B
  m=apply(data,2,mean) #C
  hist(m)
  m
}
```

### Run with same parameters as w
```{r}
m = meanclt(n = 10, iter = 10000)
```

### Mean and Variance of m
```{r}
muM = mean(m)
vM = var(m)
c(muM, vM)
```

## Task 3
### cltu function
```{r}
mycltu=function(n,iter,a=0,b=10){
## r-random sample from the uniform
y=runif(n*iter,a,b)
## Place these numbers into a matrix
## The columns will correspond to the iteration and the rows will equal the sample size n
data=matrix(y,nr=n,nc=iter,byrow=TRUE)
## apply the function mean to the columns (2) of the matrix
## these are placed in a vector w
w=apply(data,2,mean)
## We will make a histogram of the values in w
## How high should we make y axis?
## All the values used to make a histogram are placed in param (nothing is plotted yet)
param=hist(w,plot=FALSE)
## Since the histogram will be a density plot we will find the max density

ymax=max(param$density)
## To be on the safe side we will add 10% more to this
ymax=1.1*ymax
## Now we can make the histogram
hist(w,freq=FALSE,  ylim=c(0,ymax), main=paste("Histogram of sample mean",
"\n", "sample size= ",n,sep=""),xlab="Sample mean")
## add a density curve made from the sample distribution
lines(density(w),col="Blue",lwd=3) # add a density plot
## Add a theoretical normal curve 
curve(dnorm(x,mean=(a+b)/2,sd=(b-a)/(sqrt(12*n))),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
## Add the density from which the samples were taken
curve(dunif(x,a,b),add=TRUE,lwd=4)

}
```

### Explanation of function
The 2 in the apply function will make it apply on the columns of the matrix.
w is a vector of the mean of all the columns. Since there is iter columns then there are iter values in w. So if mycltu(n = 20, iter = 100000) is called, there will be 100000 values in w.

### Plots
```{r}
mycltu(n=1, iter=10000, a=0,b=10)
mycltu(n=2, iter=10000, a=0,b=10)
mycltu(n=3, iter=10000, a=0,b=10)
mycltu(n=5, iter=10000, a=0,b=10)
mycltu(n=10, iter=10000, a=0,b=10)
mycltu(n=30, iter=10000, a=0,b=10)
```

### Observation
The higher the sample size, the more normal the distribution.

## Task 4
### cltb function
```{r}
mycltb=function(n,iter,p=0.5,...){

## r-random sample from the Binomial
y=rbinom(n*iter,size=n,prob=p)
## Place these numbers into a matrix
## The columns will correspond to the iteration and the rows will equal the sample size n
data=matrix(y,nr=n,nc=iter,byrow=TRUE)
## apply the function mean to the columns (2) of the matrix
## these are placed in a vector w
w=apply(data,2,mean)
## We will make a histogram of the values in w
## How high should we make y axis?
## All the values used to make a histogram are placed in param (nothing is plotted yet)
param=hist(w,plot=FALSE)
## Since the histogram will be a density plot we will find the max density

ymax=max(param$density)
## To be on the safe side we will add 10% more to this
ymax=1.1*ymax

## Now we can make the histogram
## freq=FALSE means take a density
hist(w,freq=FALSE,  ylim=c(0,ymax),
main=paste("Histogram of sample mean","\n", "sample size= ",n,sep=""),
xlab="Sample mean",...)
## add a density curve made from the sample distribution
#lines(density(w),col="Blue",lwd=3) # add a density plot
## Add a theoretical normal curve 
curve(dnorm(x,mean=n*p,sd=sqrt(p*(1-p))),add=TRUE,col="Red",lty=2,lwd=3) 
}
```

### Plots
```{r}
mycltb(n=4,iter=10000,p=0.3)
mycltb(n=5,iter=10000,p=0.3)
mycltb(n=10,iter=10000,p=0.3)
mycltb(n=20,iter=10000,p=0.3)
```

### Plots with p=0.7
```{r}
mycltb(n=4,iter=10000,p=0.7)
mycltb(n=5,iter=10000,p=0.7)
mycltb(n=10,iter=10000,p=0.7)
mycltb(n=20,iter=10000,p=0.7)
```

### Plots with p=0.5
```{r}
mycltb(n=4,iter=10000,p=0.5)
mycltb(n=5,iter=10000,p=0.5)
mycltb(n=10,iter=10000,p=0.5)
mycltb(n=20,iter=10000,p=0.5)
```
