---
title: "Lab 10"
author: "Kaden DuBois"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks
## Task 1: Working Directory
```{r}
getwd()
```

## Task 2: Explaining mymaxlik()
### Line A and Line B
Line A: Uses outer to compute the log likelihood for each data entry in x against every possible parameter value in param and then stores them in a matrix.  
Line B: Finds the largest index of the parameter value that results in the highest log likelihood.  

### Formula for the log likelihood
$$
\ell(p) = \sum_{i=1}^{8} \left( y_i \log(p) + (20 - y_i) \log(1 - p) \right)
$$

### R code for the log likelihood
```{r}
log_likelihood <- function(p, y) {
  n <- 20  # Number of trials in each experiment
  sum(y * log(p) + (n - y) * log(1 - p))
}
```

### Maximum likelihood estimate for the given data set.
```{r}
# Given Data Set
y = c(3, 3, 4, 3, 4, 5, 5, 4)

# All possible P values
p_values <- seq(0.01, 0.99, length.out = 100)

# All possible Log Likelihood Values
log_likelihood_values <- sapply(p_values, function(p) log_likelihood(p, y))

# Plot the Log Likelihood Values
plot(p_values, log_likelihood_values, type = "l", col = "blue", lwd = 2,
     xlab = "Probability of Success (p)", ylab = "Log-Likelihood", main = "Log-Likelihood for p")

# Find the p that gives the largest log likelihood value and plot it
p_mle <- p_values[which.max(log_likelihood_values)]
abline(v = p_mle, col = "red", lwd = 2)

# Print the found p value
p_mle
```

## Task 3: mymaxlik() Example
### Radioactivity Example
```{r}
# Data from the given sample
y <- c(4, 6, 7, 6, 5)

# Log-likelihood function for Poisson
log_likelihood <- function(lambda, y) {
  -5 * lambda + sum(y) * log(lambda)
}

# All possible lambda values
lambda_values <- seq(0.1, 10, length.out = 100)

mymaxlik(log_likelihood, y, lambda_values)
```
