---
title: "Lab 7"
author: "Kaden DuBois"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks
## Task 1: Working Directory
```{r}
getwd()
```

## Task 2: Chi-Square
### The Function
```{r}
mychisim<-function(n1=10,sigma1=3,mean1=5,iter=1000,ymax=0.1,x=20, y=0.1){    # adjust ymax to make graph fit
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

ssq1=apply(data1.mat,2,var) # ssq1 is s squared

w=(n1-1)*ssq1/sigma1^2      #chi-sq stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]-1)*s^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}
```
### Plots
```{r}
# n1=10,iter=1000,μ1=10,σ1=4
  mychisim(n1 = 10, iter = 1000, mean1= 10, sigma1 = 4, ymax = 0.15)

#	n1=20,iter=1000,μ1=10,σ1=4
  mychisim(n1 = 20, iter = 1000, mean1= 10, sigma1 = 4)
  
#	n1=100,iter=1000,μ1=10,σ1=4
  mychisim(n1 = 100, iter = 1000, mean1= 10, sigma1 = 4)
  
# n1=200,iter=1000,μ1=10,σ1=4
  mychisim(n1 = 200, iter = 1000, mean1= 10, sigma1 = 4)
```

### Vector and Histogram
```{r}
chisq <- mychisim(n1 = 10, iter = 1500, mean1 = 10, sigma1 = 20)
hist(chisq$w)
```

## Task 3: T simulation
### The function
```{r}
myTsim<-function(n1=10,sigma1=3,mean1=5,iter=1000,ymax=0.1,x=2,y=0.3,...){    # adjust ymax to make graph fit
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

sd1=apply(data1.mat,2,sd) # sd
ybar=apply(data1.mat,2,mean)  # mean

w=(ybar-mean1)/(sd1/sqrt(n1))      #T stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",T," iterations= ",iter)),
xlab=expression(paste(T, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(y)-mu),s/sqrt(n1))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="T")) # some output to use if needed
}
```

### Plots
```{r}
#	n1=10,iter=1000,μ1=10,σ1=4
  myTsim(n1 = 10, iter = 1000, mean1 = 10, sigma1= 4, ymax = 0.4)

#	n1=20,iter=1000,μ1=10,σ1=4
  myTsim(n1 = 20, iter = 1000, mean1 = 10, sigma1= 4, ymax = 0.4)
  
#	n1=100,iter=1000,μ1=10,σ1=4
  myTsim(n1 = 100, iter = 1000, mean1 = 10, sigma1= 4, ymax = 0.5)
  
#	n1=200,iter=1000,μ1=10,σ1=4
  myTsim(n1 = 200, iter = 1000, mean1 = 10, sigma1= 4, ymax = 0.5)
```

### Vector and Histogram
```{r}
T <- myTsim(n1= 10, iter = 1500, mean1 = 20, sigma1 = 10, ymax = 0.5)
hist(T$w)
```

## Task 4: Chi-Square with 2 populations
### The function
```{r}
mychisim2<-function(n1=10,n2=14,sigma1=3,sigma2=3,mean1=5,mean2=10,iter=1000,ymax=0.07,x=40,y=0.04,...){    # adjust ymax to make graph fit
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=(n1+n2-2)*spsq/(sigma1^2)#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]+n[2]-2)*S[p]^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}
```

### Plots
```{r}
#	n1=10,n2=10,μ1=5,μ2=10,σ1=σ2=4,iter=1000
  mychisim2(n1 = 10, n2 = 10, mean1 = 5, mean2 = 10, sigma1 = 4, sigma2 = 4, iter = 1000)

#	n1=20,n2=10,μ1=3,μ2=5,σ1=σ2=10,iter=1000
  mychisim2(n1 = 20, n2 = 10, mean1 = 3, mean2 = 5, sigma1 = 10, sigma2 = 10, iter = 1000)
  
#	n1=50,n2=50,μ1=5,μ2=10,σ1=σ2=4,iter=10000
  mychisim2(n1 = 50, n2 = 50, mean1 = 5, mean2 = 10, sigma1 = 4, sigma2 = 4, iter = 10000)
  
#	n1=80,n2=50,μ1=3,μ2=5,σ1=σ2=10,iter=10000
  mychisim2(n1 = 80, n2 = 50, mean1 = 3, mean2 = 5, sigma1 = 10, sigma2 = 10, iter = 10000)
```

### Vector and Histogram
```{r}
chisq2 <- mychisim2(iter = 10000)
hist(chisq2$w)
```

## Task 5: T simulation with 2 populations
### The function
```{r}
myTsim2<-function(n1=10,n2=14,sigma1=3,sigma2=3,mean1=5,mean2=10,iter=1000,ymax=0.5,x=2,y=0.4,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ybar1= apply(data1.mat,2,mean)
ssq2=apply(data2.mat,2,var)
ybar2=apply(data2.mat,2,mean)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=((ybar1-ybar2)-(mean1-mean2))/sqrt(spsq*(1/n1+1/n2))#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",T)),
xlab=paste(" T Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(Y)[1]-bar(Y)[2])-(mu[1]-mu[2]),S[p]*sqrt(frac(1,n[1])+frac(1,n[2])))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sdw=sd(w),fun="T")) # some output to use if needed
}
```

### Plots
```{r}
#	n1=10,n2=10,μ1=5,μ2=10,σ1=σ2=4,iter=1000
  myTsim2(n1 = 10, n2 = 10, mean1 = 5, mean2 = 10, sigma1 = 4, sigma2 = 4, iter = 1000)

#	n1=20,n2=10,μ1=3,μ2=5,σ1=σ2=10,iter=1000
  myTsim2(n1 = 20, n2 = 10, mean1 = 3, mean2 = 5, sigma1 = 10, sigma2 = 10, iter = 1000)
  
#	n1=50,n2=50,μ1=5,μ2=10,σ1=σ2=4,iter=10000
  myTsim2(n1 = 50, n2 = 50, mean1 = 5, mean2 = 10, sigma1 = 4, sigma2 = 4, iter = 10000)
  
#	n1=80,n2=50,μ1=3,μ2=5,σ1=σ2=10,iter=10000
  myTsim2(n1 = 80, n2 =50, mean1 = 3, mean2 = 5, sigma1 = 10, sigma2 = 10, iter = 10000)
```

### Vector and Histogram
```{r}
T2 <- myTsim2(iter = 10000)
hist(T2$w)
```

## Task 6: F simulation with 2 populations
### The function
```{r}
myFsim2<-function(n1=10,n2=14,sigma1=3,sigma2=2,mean1=5,mean2=10,iter=1000,ymax=0.9,x=6,y=0.5,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
#spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=ssq1*sigma2^2/(ssq2*sigma1^2) #
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",F)),
xlab=paste("F Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(df(x,n1-1,n2-1),xlim=c(0,6),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(F==frac(s[1]^2,s[2]^2)*frac(sigma[2]^2,sigma[1]^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="F")) # some output to use if needed
}
```

### Plots
```{r}
#	n1=10,n2=10,μ1=5,μ2=10,σ1=σ2=4,iter=1000
  myFsim2(n1 = 10, n2 = 10, mean1 = 5, mean2 = 10, sigma1 = 4, sigma2 = 4, iter = 1000)

#	n1=20,n2=10,μ1=3,μ2=5,σ1=σ2=10,iter=1000
  myFsim2(n1 = 20, n2 = 10, mean1 = 3, mean2 = 5, sigma1 = 10, sigma2 = 10, iter = 1000)
  
#	n1=50,n2=50,μ1=5,μ2=10,σ1=σ2=4,iter=10000
  myFsim2(n1 = 50, n2 = 50, mean1 = 5, mean2 = 10, sigma1 = 4, sigma2 = 4, iter = 10000, ymax = 1.6)
  
#	n1=80,n2=50,μ1=3,μ2=5,σ1=σ2=10,iter=10000
  myFsim2(n1 = 80, n2 =50, mean1 = 3, mean2 = 5, sigma1 = 10, sigma2 = 10, iter = 10000, ymax = 1.6)
```

### Vector and Histogram
```{r}
F <- myFsim2(iter = 10000)
hist(F$w)
```

## Task 7: Adding Data to R package
```{r}
library(MATH4753KADEDUB)
data("fire")
knitr::kable(head(fire))
```